Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-30 paper/ms.tex
nuevo orden en las figuras

@@

@@

\begin{figure}

  \includegraphics[width=0.47\textwidth]{fig5.pdf}
\caption{ Angular Correlation functions for $\log M_{\rm
    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
  M$.  
  The shaded region represents the 1-sigma deviation due to cosmic
  variance. Radical different models in $\Delta M$ are consistent with
  observations once cosmic variance is modelled in detail.}
\label{fig:corr}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=0.47\textwidth]{fig5.pdf}
\caption{ Angular Correlation functions for $\log M_{\rm
    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
  M$.  
  The shaded region in the models represents the $1-\sigma$ variation
  due to cosmic variance. Radical different models in $\Delta M$ are consistent with
  observations once cosmic variance is modelled in detail.} 
\label{fig:corr}
\end{figure}

@@

Fig. \ref{fig:corr} shows the observational ACF by
\citet{Bielby16} compared to the ACF in three different models with a
wide range in $\dm$.  
This already shows that radically different models can be compatible
with observations once cosmic variance uncertainties are modelled in
detail.

@@
